### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@1e9ee1acde888d3196c7d683b515b6fcb26423cc 🚀

Interactions between plants and pollinators create networks of
interactions, which together form the ``architecture of biodiversity''
(Bascompte \& Jordano 2007). The functioning and stability of ecosystems
emerge from these interactions, but anthropogenic change threatens to
unravel and ``rewire'' these interaction networks (CaraDonna \emph{et
al.} 2017), threatening the persistence of these systems.
Plant-pollinator networks face two possible forms of rewiring in
response to anthropogenic environmental change: spatial and temporal.
Spatially, range shifts could cause interacting species to no longer
overlap in space, and shifts in phenology could cause interacting
species to no longer occur at the same time of year. This chapter uses
several years of data on bumblebee-flower phenology and interactions
across several field sites, each consisting of several plots across an
elevational gradient, combined with spatial records of species
occurrence via GBIF to forecast the uncoupling of the plant-pollinator
metaweb of Colorado.

@@

The data for this chapter is derived from multiple sources that can be
split into four categories. (1) Field data from three different field
sites across Colorado, each with multiple plots across an elevational
gradient, for seven, seven, and three years respectively. This data was
collected by Paul CaraDonna and Jane Oglevie (from the Rocky Mountain
Biological Laboratory; RMBL) and Julian Resasco (CU Boulder). (2) GBIF
spatial occurrence records of each of these species across Colorado,
including a metaweb of interactions across all of Colroado taken from
GBIF. (3) Remotely sensed data consisting of current and forecasting
bioclimatic variables from CHELSA. (4) Phylogenies for both bee and
flower species derived from NCBI GenBank barcodes for mitochondrial COI
(bumblebees) and chloroplast rbcL (flowers).

>>>>

Interactions between plants and pollinators form networks which together
structure the ``architecture of biodiversity'' (Bascompte \& Jordano
2007). The functioning and stability of ecosystems emerge from these
interactions, but anthropogenic change threatens to unravel and
``rewire'' these interaction networks (CaraDonna \emph{et al.} 2017),
jeopardizing the persistence of these systems. Plant-pollinator networks
face two possible forms of rewiring in response to anthropogenic
environmental change: spatial and temporal. Range shifts could cause
interacting species to no longer overlap in space, and shifts in
phenology could cause interacting species to no longer occur at the same
time of year. This chapter uses several years of data on
bumblebee-flower phenology and interactions across several field sites,
each consisting of several plots across an elevational gradient,
combined with spatial records of species occurrence via GBIF to forecast
the uncoupling of the plant-pollinator metaweb of Colorado.

@@

The data for this chapter is derived from multiple sources that can be
split into four categories. (1) Field data from three different field
sites across Colorado, each with multiple plots across an elevational
gradient, for seven, seven, and three years respectively. This data was
collected by Paul CaraDonna and Jane Oglevie (from the Rocky Mountain
Biological Laboratory; RMBL) and Julian Resasco (CU Boulder). (2) GBIF
spatial occurrence records of each of these species across Colorado,
including a metaweb of interactions across all of Colorado taken from
GBIF. (3) Remotely sensed data consisting of current and forecasting
bioclimatic variables from CHELSA. (4) Phylogenies for both bee and
flower species derived from NCBI GenBank barcodes for mitochondrial COI
(bumblebees) and chloroplast rbcL (flowers).
